### 2019-05-23 paper/spad_single/sections/method.tex
Working on the paper.

\subsection{Monocular Depth Estimation}

\subsection{Global Depth Hints}

\begin{itemize}
	\item image formation model	
	\item training details
	\item simulations and comparison: qualitative and quantitative
\end{itemize}

>>>>

In this section, we describe the histogram formation model for a single-pixel
time-of-flight lidar sensor under diffuse, pulsed laser illumination. We also use
this model to simulate the formation of a histogram given a depth map. 
\subsection{Histogram Formation Model}
Consider a laser which emits a pulse at time $t = 0$ with shape $g(t)$. The waveform passes through a diffuser
which spreads the light evenly over some 3D scene $z(x,y)$, which we describe as
depth as a function of $(x,y)$ position. 
To assess the distribution of returning photons from the whole scene, we first consider photons returning from a single
location $(x, y)$. The expected number of photon events detected 
from this location in the time interval $(t, t + \Delta t)$ is given as
\begin{equation}
  \lambda_{x,y}[n] = \int_{n\Delta t}^{(n+1) \Delta t} (f * g)\paren*{t - 2z(x,y)/c} dt. \label{single_loc_spad} 
\end{equation}

where $c$ is the speed of light, and $f$ models the temporal uncertainty in the
detector. Since the detection of each photon can be described as a Bernoulli random variable,
the total number of accumulated photons in this time interval follows a Poisson
distribution according to

\begin{equation}
  h[n] \sim \mathcal{P}\paren*{\sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + d} \label{global_hints}
\end{equation}

where $\alpha_{x,y} = r_{x,y}/z(x,y)^2$ captures the attenuation of the
photon counts due to the reflectance $r(x,y)$ of the scene and due to the
inverse square falloff $1/z(x,y)^2$.
In addition, $\eta$ is the detection probability of a photon
triggering a SPAD event, and $d = \eta a + b$ is the number of ambient photons $a$
and the number of ``dark count'' events $b$, which is a property of the SPAD.

Pick an example scene, show side-by-side with depth map and histogram of gt
depth and histogram from SPAD (to make intuitive)

\subsection{Monocular depth estimation with global depth hints}
Given a single RGB image $I(x,y)$ and a histogram of photon arrivals $h[n]$
collected as in equation \ref{global_hints}, we seek to
reconstruct the ground truth depth map $z(x,y)$.
Our method has two parts. First, we initialize our estimate of the depth map from the single RGB
image via a monocular depth estimator. Second, we refine this depth map using
the captured histogram $h[n]$ via a process we call Differentiable Histogram Matching.
Differentiable histogram matching as a tool for post-processing the image to
match the depth map to the statistics we capture from the SPAD.

\paragraph{Initialization via CNN}
Convoluational Neural Networks have become increasingly capable of leveraging
monocular depth cues from to produce accurate estimates of depth
from only a single image. We therefore choose to initialize our depth map
estimate $z^{(0)}(x,y)$ using
a CNN. However, any depth estimator reliant on only a single
view will be unable resolve the inherent scale ambiguity in the scene resulting
from the tradeoff between size of and distance to an object. Our next step,
differentiable histogram matching, will resolve this ambiguity using the depth
information present in the SPAD histogram.

\paragraph{Differentiable Histogram Matching}
Given our initial depth map estimate, our goal is now to refine that depth map
so that it agrees with the information provided by the SPAD histogram.
Figure showing just the differentiable histogram matching part of the model.
At a high level, our goal is to formulate the SPAD histogram formation model as
a differentiable function of the depth map and RGB image so that the output
$\hat h[n]$ of the SPAD simulation can be compared to the observed SPAD
histogram $h[n]$ and the depth map can be optimized via gradient descent or
other first-order method.
Given per-pixel depth, we can simulate SPAD histogram formation using equation
\ref{global_hints}, where we approximate $\lambda_{x,y}[n]$ using Kernel Density
Estimation as:
\begin{equation}
  \hat \lambda^{(i)}_{x,y}[n] = \frac{1}{\sigma\sqrt{2 \pi}}\exp\paren*{-\frac{1}{2\sigma^2}(n - \hat z^{(i)}(x,y))} \label{KDE}
\end{equation}
where $\hat z^{(i)}(x, y)$ is our estimate of the depth at pixel $(x,y)$ at
iteration $i$.

Once we have $\lambda^{(i)}$, we compute $\hat h[n]$ according to the rest of
the SPAD histogram formation model, neglecting the Poisson sampling, as follows
\begin{equation}
  \hat h[n] = \sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + d \label{diff_forward}
\end{equation}
model. (Explain where $d$ and $\eta$ come from.)
Finally, given two histograms, we can compute the Sinkhorn Distance between
them. As described in \ref{Cuturi et. al.}, the Sinkhorn Distance is a measure
of distance between two probability distributions. It is particularly desirable
to us because unlike other distances between probability distributions, such as
the KL divergence or the simple RMSE, the Sinkhorn Distance scales with
separation as well as magnitude. Furthermore, unlike the Wasserstein Distance
from which it is derived, the computation of the Sinkhorn Distance can be
computed via Sinkhorn Iterations, which are fast and differentiable.
We refer the reader to \ref{Cuturi et. al.} for the details.
``Minimize blah s.t. blah blah''
\subsection{``How you actually solve it''}

\subsection{Implementation Details}
For the Monocular Depth Estimator, we use a pretrained version of the
the Deep Ordinal Regression Network (DORN) \cite{}. We use the implementation of
the Sinkhorn Iteration (for calculating the entropy-regularized Wasserstein
Loss) from \ref Cuturi et. al. We update the depth map using gradient descent.
Everything is implemented in PyTorch.

Table with hyperparameters (defer to supplementary info?)
- Kernel Density Estimation (sigma)
- Sinkhorn Iterations (maximum number, epsilon tolerance)
- Gradient Descent (learning rate, epsilon tolerance, max iterations)
